STR: Seasonal-Trend decomposition using Regression

### 2020-11-17 str_ijds.Rmd
Added Rmarkdown ref and link to new github repo

An R package, **stR** [@stR], implementing our model is available on CRAN.
The package also contains a vignette, which describes various practical aspects of the implementation in detail. The calculations and the plots presented in this article can be reproduced using the code available from \url{https://bit.ly/str_ijds}.

>>>>

An R package, **stR** [@stR], implementing our model is available on CRAN.
The package also contains a vignette, which describes various practical aspects of the implementation in detail.

This paper was produced using Rmarkdown [@rmarkdown]. The source files to reproduce the paper, including all the examples, are available from [`github.com/robjhyndman/STR_paper`](https://github.com/robjhyndman/STR_paper).

### 2020-11-17 str_ijds.tex
Added Rmarkdown ref and link to new github repo

An R package, \textbf{stR} \autocite{stR}, implementing our model is available on CRAN.
The package also contains a vignette, which describes various practical aspects of the implementation in detail. The calculations and the plots presented in this article can be reproduced using the code available from \url{https://bit.ly/str_ijds}.

>>>>

An R package, \textbf{stR} \autocite{stR}, implementing our model is available on CRAN.
The package also contains a vignette, which describes various practical aspects of the implementation in detail.

This paper was produced using Rmarkdown \autocite{rmarkdown}. The source files to reproduce the paper, including all the examples, are available from \href{https://github.com/robjhyndman/STR_paper}{\texttt{github.com/robjhyndman/STR\_paper}}.
